Open archaeology, open source?

### 2024-02-02 analysis/_04-open_archaeology.qmd
Encode percentages in section 4

```{r data-merge-categories}
# Merge smaller categories for subsequent analyses
oarch <- mutate(
  oarch,
  category = recode(
    category,
    "Specifications, protocols and schemas" = "Other documents",
    "Products" = "Other documents",
    "Guides" = "Other documents",
    .default = category
  ),
  category = factor(
    category, 
    c("Packages and libraries", 
      "Standalone software",
      "Scripts",
      "Lists and datasets",
      "Other documents")
  )
)
```

```{r num-p_platform}
p_platform <- sum(!is.na(oarch$platform)) / nrow(oarch)
```

In our breakdown of open-archaeo by category (see @tbl-categories), we demonstrate the pervasiveness of various development models, and the requisite technical capabilities that developers assume users hold.
Most resources (`r percent(p_platform)`) included in open-archaeo are designed to be used atop an existing "platform" -- for example a package that extends a programming language or a plugin for an application.
The designers of this code are basically creating additional functions within the base platform that are useful for archaeological purposes.
Others create standalone software <!-- percent --> that can be run independently of such platforms, for example desktop or web apps.
A significant number of projects also comprise of datasets <!-- percent --> and non-packaged code snippets <!-- percent --> that have been made available for general use.

>>>>

```{r data-categories-platforms}
# Merge smaller categories for subsequent analyses
oarch <- mutate(
  oarch,
  category = recode(
    category,
    "Specifications, protocols and schemas" = "Other documents",
    "Products" = "Other documents",
    "Guides" = "Other documents",
    .default = category
  ),
  category = factor(
    category, 
    c("Packages and libraries", 
      "Standalone software",
      "Scripts",
      "Lists and datasets",
      "Other documents")
  )
)

n_platform <- sum(!is.na(oarch$platform))
p_platform <- n_platform / nrow(oarch)

n_standalone <- nrow(filter(oarch, category == "Standalone software"))
p_standalone <- n_standalone / nrow(oarch)

n_datasets <- nrow(filter(oarch, tag1 == "Datasets" | tag2 == "Datasets" | 
                            tag3 == "Datasets" | tag4 == "Datasets" | 
                            tag5 == "Datasets"))
p_datasets <- n_datasets / nrow(oarch)

n_scripts <- nrow(filter(oarch, category == "Scripts"))
p_scripts <- n_scripts / nrow(oarch)
```

In our breakdown of open-archaeo by category (see @tbl-categories), we demonstrate the pervasiveness of various development models, and the requisite technical capabilities that developers assume users hold.
Most resources (`r percent(p_platform)`) included in open-archaeo are designed to be used atop an existing "platform" -- for example a package that extends a programming language or a plugin for an application.
The designers of this code are basically creating additional functions within the base platform that are useful for archaeological purposes.
Others create standalone software (`r percent(p_standalone)`) that can be run independently of such platforms, for example desktop or web apps.
A significant number of projects also comprise of datasets (`r percent(p_datasets)`) and non-packaged code snippets (`r percent(p_scripts)`) that have been made available for general use.
